Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment

### 2024-07-31 JASA-template.tex
Response to elicitation of P.

Now, based on this notion of abstaining from selecting a predictor, we can perform
a sensitivity analysis over a set of priors on the prior selection probability.
That is, we can consider a set of possible values for $q$ such that
$q\in\mathcal{P}$, where $\mathcal{P} \subseteq \left(0, 1\right)^{p}$.
Here, the equality occurs for the near vacuous case. However, in real-life
situations, performing a robust Bayesian analysis for the near vacuous case is 
not practical. Instead, we incorporate expert elicitation to define our model.
For instance, we can consider $q\in \left[\underline{q}, \overline{q}\right]$
where $p\underline{q}$ and $p\overline{q}$ represent the bounds of the prior expectation on the
total number of variables present in either of the models.

@@

\paragraph{Elicitation}
One way to elicit $\mathcal{P}$
is through a prior expected bound on the number of active predictors.
Although we may do so directly,
we may alternatively also use the empirically observed correlations from the data directly.
This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
When doing so, we need \added{a prior judgement on what is a reasonable} correlation between active predictors and the outcome.

So, say we judge, through expert elicitation, that
an active predictor has a correlation with the outcome
that is typically between $0.15$ and $0.35$.
Let $p_1$ be the number of predictors with marginal correlation greater than $0.15$
and let $p_2$ be number of predictors with marginal 
correlation greater than $0.35$.
Then $\mathcal{P}=[p_2/p , p_1/p]$ (note that $p_2\le p_1$) gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.

>>>>

Now, based on this notion of abstaining from selecting a predictor, we can perform
a sensitivity analysis over a set of priors on the prior selection probability.
That is, we can consider a set of possible values for $q$ such that
$q\in\mathcal{P}$, where $\mathcal{P} \subseteq \left(0, 1\right)^{p}$.
Here, the equality occurs for the near vacuous case. However, in real-life
situations, performing a robust Bayesian analysis for the near vacuous case is 
not practical. Instead, we incorporate expert elicitation to define our model.

\added{%
For instance, assume $\underline{k}$ and $\overline{k}$ represent the expert's bounds of the prior expectation on the
total number of variables present in either of the models. We can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
}

\added{%
We may also use the empirically observed correlations from the data directly.
This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
When doing so, we need
% \added{
a prior judgement on what is a reasonable
%}
correlation between active predictors and the outcome.
Say the expert judges that
an active predictor has a correlation with the outcome
that is typically between $\underline{c}$ and $\overline{c}$.
Let $\overline{k}$ be the number of predictors with marginal correlation greater than $\underline{c}$
and $\underline{k}$ be number of predictors with marginal 
correlation greater than $\overline{c}$.
%%% MT to TB: in retrospect, using \underline{k} to lower bound the
%%% number of active variables is a bit strange... it seems like we're
%%% treating variables with "too high" correlations as inactive;
%%% should we simply set \underline{k} directly (e.g. 0, 1, or higher
%%% if suitable) instead of using the correlations?
As before, we can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
}

@@

\paragraph{Elicitation}

\added{%
To elicit $\mathcal{P}$,
as discussed earlier,
we use the empirically observed correlations from the data directly.
We assume that, through expert elicitation,
an active predictor has a correlation with the outcome
that is typically between $0.15$ and $0.35$.
Let $\overline{k}$ be the number of predictors with marginal correlation greater than $0.15$
and let $\underline{k}$ be number of predictors with marginal 
correlation greater than $0.35$.
Then $\mathcal{P}=[\underline{k}/p , \overline{k}/p]$ gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.%
}
